Convective penetration probably parameterizes convective overshoot

### 2021-07-19 manuscript/ms.tex
some changes to abstract and intro; need more

\begin{abstract}
Most stars host convection zones in which heat is transported directly by fluid motion.
Parameterizations like mixing length theory adequately describe convective flows in the bulk of these regions, but the behavior of convective boundaries is not well understood.
Here we examine how convective motions mix entropy and in turn extend the size of the convection zone, a process referred to as convective penetration.
We derive a ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
Following \citet{roxburgh1989} and \citet{zahn1991}, we construct a model of penetration based on an energy balance, and find that the extent of penetration is controlled by $\mP$.
We perform 3D numerical simulations with Dedalus using a simplified Boussinesq model of stellar convection with a radiative flux and find good agreement with the derived theory.
We evolve these simulations for thousands of overturn times; over these long timescales our simulations consistently develop large penetrative regions.
In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by (TODO X amount for some choice of parameters).
We further discuss prospects for extending these results to more realistic stellar contexts.
\end{abstract}
\keywords{UAT keywords}

@@

Studies which more closely model the conditions inside of stars have presented confusing results.
Many studies have exhibited hints of penetrative convection -- that is, mixing of the entropy gradient towards the adiabatic beyond the convective boundary \citep{hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, browning_etal_2004, rogers_etal_2006, kitiashvili_etal_2016, brun_etal_2017, pratt_etal_2017, higl_etal_2021}.
These simulations include simple plane-parallel studies of compressible convection as well as global 3D simulations which employ profiles from stellar structure codes as background states.
Unfortunately, other fundamental studies in both Cartesian and spherical geometries have exhibited little to no dependence of penetration on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.

@@

\begin{acknowledgments}
We thank Keaton Burns, Matt Browning, Matteo Cantiello and Kyle Augustson for useful discussions and questions which improved the content of this manuscript.
EHA is funded as a CIERA Postdoctoral fellow and would like to thank CIERA and Northwestern University. 
We acknowledge the hospitality of Nordita during the program ``The Shifting Paradigm of Stellar Convection: From Mixing Length Concepts to Realistic Turbulence Modelling," where the groundwork for this paper was set.
This work was supported by NASA HTMS grant 80NSSC20K1280.
Computations were conducted with support from the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s2276.
The Flatiron Institute is supported by the Simons Foundation.
\end{acknowledgments}

>>>>

\begin{abstract}
Most stars host convection zones in which heat is transported directly by fluid motion.
Parameterizations like mixing length theory adequately describe convective flows in the bulk of these regions, but the behavior of convective boundaries is not well understood.
Here we examine how convective motions efficiently mix entropy in the radiative zone.
We present 3D numerical simulations which exhibit penetration zones: regions where the entire luminosity \emph{could} be carried by radiation, but where the temperature gradient is approximately adiabatic and convection is present.
To parameterize this effect, we define the ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
Following \citet{roxburgh1989} and \citet{zahn1991}, we construct an energy-based model in which the extent of penetration is controlled by $\mP$.
We conduct 3D simulations with Dedalus using a simplified Boussinesq model of stellar convection including a radiative flux, and we find good agreement between simulations and the derived theory.
We evolve these simulations for thousands of overturn times; over these long timescales our simulations consistently develop large penetrative regions.
In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by $\sim$35\% of a pressure scale height.
We discuss prospects for extending these results to more realistic stellar contexts.
\end{abstract}
\keywords{UAT keywords}

@@

Studies which more closely model the conditions inside of stars have presented confusing results.
Many studies have exhibited hints of penetrative convection -- that is, the mixing of the entropy towards an adiabatic profile beyond the convective boundary.
Some of these studies exhibit dynamical or flux-based hints of penetration (the convective flux is negative and the radiative flux carries more than the total flux going through the simulation), but do not clearly report the value of the entropy gradient \citep{hurlburt_etal_1986, singh_etal_1995, browning_etal_2004, brun_etal_2017, pratt_etal_2017}
Others report a change of the entropy gradient towards the adiabatic beyond the convecting region \citep{hurlburt_etal_1994, saikia_etal_2000, rogers_etal_2006, kitiashvili_etal_2016}
Some simulations show little evidence of true penetration \citep[see e.g., the superadiabaticity profiles of][]{higl_etal_2021}.
These simulations include simple plane-parallel studies of compressible convection as well as global 3D simulations which employ profiles from stellar structure codes as background states.
Unfortunately, other fundamental studies in both Cartesian and spherical geometries have exhibited little to no dependence of penetration on the stiffness \citep{brummell_etal_2002, rogers_glatzmaier_2005}.
This host of experiments suggests that convective penetration is \emph{probably} a process that happens in stars, but no clear model has emerged which explains whether convective penetration depends on stiffness or some other quantity.

@@

\begin{acknowledgments}
We thank Keaton Burns, Matt Browning, Matteo Cantiello and Kyle Augustson for useful discussions and questions which improved the content of this manuscript.
EHA is funded as a CIERA Postdoctoral fellow and would like to thank CIERA and Northwestern University. 
We acknowledge the hospitality of Nordita during the program ``The Shifting Paradigm of Stellar Convection: From Mixing Length Concepts to Realistic Turbulence Modelling," where the groundwork for this paper was set.
This work was supported by NASA HTMS grant 80NSSC20K1280 and NASA SSW grant 80NSSC19K0026.
Computations were conducted with support from the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s2276.
The Flatiron Institute is supported by the Simons Foundation.
\end{acknowledgments}
